Nic Steyn

### 2025-03-11 site/papers.qmd
update paper list

@@

>>>>

**Steyn, N.**, Chadeau-Hyam, M., Whitaker, M., et al. Pandemic-risk-related behaviour change in England from June 2020 to March 2022: REACT-1 study among over 2 million people. *medRxiv preprint*. [https://doi.org/10.1101/2025.03.03.25323250](https://doi.org/10.1101/2025.03.03.25323250)

@@

[Pandemic-risk-related behavioural data portal](https://m-whit-ic.shinyapps.io/react-social-shiny/): an R shiny server hosting a large quantity of aggregated data on pandemic-risk-related behaviours in England, collected as part of the REACT-1 study. By making these data publicly available, we hope to enable further research. Methodology can be found in our [preprint](https://doi.org/10.1101/2025.03.03.25323250).
